Nail: A practical interface generator for data formats

### 2014-08-14 paper/osdi14/relwk.tex
Related work (de-anonymized citation)
Cite DataScript

Closely related work has been done in the field of data description languages, for example
PacketTypes~\cite{mccann2000packet} and DataScript~\cite{DataScript}. However, PacketTypes works
only as a parser, not as an output generator. Data description languages typically are not as
expressive as parsing expression grammars (PEGs), but rather implement a C-like structure model
enhanced with length fields and constraints. These systems also cannot handle complicated encodings
such as compressed data, which are supported by Nail's stream transforms.

@@

We presented an earlier design of Nail at a
workshop~\cite{bangert:nail-langsec-anon}.  At that stage, Nail had only
limited support for dependent fields, and did not support stream
transforms at all, which are crucial for supporting real-world formats
like DNS and ZIP\@.  The workshop paper also did not provide a detailed
design discussion or evaluation.

>>>>

Closely related work has been done in the field of data description languages, for example
PacketTypes~\cite{mccann2000packet} and DataScript~\cite{DataScript}. However, PacketTypes works
only as a parser, not as an output generator and implement a C-like structure model enhanced with
length fields and constraints. DataScript adds output generation and built-in support for offset
fields. However, these systems cannot handle complicated encodings such as compressed data, which
are supported by Nail's stream transforms. Many built-in features of these date description
languages, such as the various ways of encoding array size or length and offsets, can be expressed
by Nail transformations, keeping the core language itself smaller and increasing flexibility.

@@

We presented an earlier design of Nail at a
workshop~\cite{bangert:nail-langsec}.  At that stage, Nail had only
limited support for dependent fields, and did not support stream
transforms at all, which are crucial for supporting real-world formats
like DNS and ZIP\@.  The workshop paper also did not provide a detailed
design discussion or evaluation.
